\LaTeXe\ guide for the Journal of Functional Programming

### 2019-05-02 papers/jfp/7-experience.tex
Fix two typos, drop repeated text
Add examples to S7.4

We have also got the GHC build working with \Cloud \Shake, resulting in build
times of 3m and 30s instead of 1h and 8m (on Windows). Due to aspects like slow
and fully sequential \cmd{configure} we do not see the dramatic reductions
reported by Standard Chartered. Converting to a build suitable for sharing is
not overly onerous, but nor is it trivial. Some things that require attention:

\begin{itemize}
\item \textbf{Irrelevant differences}: A common problem is that you do not get
      shared caching when you want it. To get caching, it is important that all
      machines are identical for the aspects that involve the build system. In
      particular, that means that all paths must be relative, and all
      dependencies on system binaries (e.g. \cmd{gcc}) should either be
      controlled by the build system (e.g. using \Nix) or have tolerance to
      account for minor machine variations.
\item \textbf{Insufficient produced files}: A build rule must declare all files
      it produces, so these are stored in the cache and can be restored from the
      cache. If you do not use a remote cache then it is permissible to have
      files not known to the build system which change at the same time as files
      that are known. Once using a remote cache any file that is produced as a
      side-effect of a rule and then later used \emph{must} be declared. Failure
      to declare such files means that if some step produces a file, and a later
      step relies on it, that step breaks. In practice, most issues encountered
      during the move to cloud builds for GHC were a lack of declared produced
      files.
\item \textbf{Insufficient dependencies}: While insufficient dependencies are
      often a problem, the move to a cloud build makes them even more critical,
      as missing dependencies are likely to mean a result is \emph{never built
      locally}, rather than just build locally only once. Furthermore,
      dependencies in a cloud setting must be more complete. For example, using
      the build system from Fig.~\ref{fig-make}, with a local build system
      without early cutoff, if the rule to produce \cmd{main.exe} also made use
      of \cmd{main.c} but did not declare so, that is not a problem. With the
      addition of early cutoff, if \cmd{main.c} changes in an important way but
      \cmd{main.o} is not rebuilt that causes issues, but is a somewhat rare
      occurrence. With cloud builds that becomes somewhat more common.
\end{itemize}

>>>>

% We have also got the GHC build working with \Cloud \Shake, resulting in build
% times of 3m and 30s instead of 1h and 8m (on Windows). Due to aspects like slow
% and fully sequential \cmd{configure} we do not see the dramatic reductions
% reported by Standard Chartered.

Converting to a build suitable for sharing is
not overly onerous, but nor is it trivial. Some things that require attention:

\begin{itemize}
\item \textbf{Irrelevant differences}: A common problem is that you do not get
      shared caching when you want it. As one example, imagine two users install
      \cmd{gcc} on different paths (say \cmd{/usr/bin} and \cmd{/usr/local/bin})
      -- if these paths are recorded by the build system the users won't share
      cache entries. As another example, consider a compiler that embeds the current time
      in the output -- any users who build that file locally won't get any shared
      caching of subsequent outputs. Possible solutions include using relative paths,
      depending only on version numbers for system binaries (e.g. \cmd{gcc}),
      controlling the environment closely (e.g. using \Nix) and extra flags to
      encourage compilers to be more deterministic.
\item \textbf{Insufficient produced files}: A build rule must declare all files
      it produces, so these can be included in the cache.
      As an example using Haskell, compilation of \cmd{Foo.hs} produces
      \cmd{Foo.hi} and \cmd{Foo.o}. If you declare the rule as producing \cmd{Foo.hi},
      and only ever depend on \cmd{Foo.hi}, but \emph{use} \cmd{Foo.o} after
      depending on \cmd{Foo.hi}, a local build will probably work. However,
      if \cmd{Foo.hi} is downloaded from a remote cache, \cmd{Foo.o} will not be present,
      and subsequent commands may fail (e.g. linking). In practice, most issues encountered
      during the move to cloud builds for GHC were caused by failing to declare produced
      files.
\item \textbf{Insufficient dependencies}: While insufficient dependencies are
      always a problem, the move to a cloud build makes them even more serious.
      If you omit a dependency on a file that changes rarely, each developer will
      have built it locally at least once, and more regularly if they ever do clean
      builds. In contrast, with a cloud build, the file might only be built
      \emph{just once}, and reused forevermore. If things go wrong, a clean build
      is no longer a refuge of last resort.
\end{itemize}
